Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Use of cannot and another instead of can not and an other

Another use case they can not express is to buy either one or the other item but not both. An economist would describe this as two substitute goods. A simple example for this is when you want to buy a ticket from Vienna to Munich but you do not care if you are going by train or by plane.

@@

Another issue with this kind of auction is that if someone's primary goal is one item and its price is rising too high he or she may be also satisfied with an other item instead. Again, this case is not possible in sequential auctions without speculation.

@@

When the offer phase is completed the seller has a set of all bids $B = {<b_i,p_i>}$. From this set they chose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good can not be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : <b_i,p_i> \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}

>>>>

Another use case they cannot express is to buy either one or the other item but not both. An economist would describe this as two substitute goods. A simple example for this is when you want to buy a ticket from Vienna to Munich but you do not care if you are going by train or by plane.

@@

Another issue with this kind of auction is that if someone's primary goal is one item and its price is rising too high he or she may be also satisfied with another item instead. Again, this case is not possible in sequential auctions without speculation.

@@

When the offer phase is completed the seller has a set of all bids $B = {<b_i,p_i>}$. From this set they chose that subset of them which maximizes profit and is satisfiable. In essence satisfiability means that the same good cannot be sold more than once. Profit maximization computes for each satisfiable allocation $L \subset B$ the total value $v(L) = \sum \{p_i : <b_i,p_i> \subset L\}$ and chooses the maximum.\footnote{As explained in the first section there may be other objectives beside or instead of profit maximization in the auction but in commercial auctions the auctioneer's revenue is the main goal. So we will not provide further details for these expansions.}
